\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
done with experiments, now I am on the case study.

\subsection{Remote control mode}
\fengwei{In BadUSB-C section, remote control model is after privacy extraction mode.}

To test the capability of remote control mode, we chose \textit{iPad Pro (3rd
	generation)}, a tablet in iOS 14.3 with a USB Type-C interface, as the target
device in this experiment.  Besides disguising as normal HID devices like a
conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
stream from the target device to the attacker via WiFi.  After the connection
establishment, the attacker performed a series actions to test the capability of
\tool. In the beginning, the attacker accessed album application on the iPad and
obtained all the photos inside. After that, the attacker sent messages via victim's
account. At last, the attacker performed a transaction using the
financial application. All of these tests resulted in success.

Through this experiment, we have found that with video transmission and mouse
emulation, \tool extensively expanded the attack capability of BadUSB,
especially in mobile devices. We have archived the complete hijack of the victim's
device in this experiment.

>>>>

\subsection{Fully Control Mode}
%\fengwei{In BadUSB-C section, remote control model is after privacy extraction mode.}

To test the capability of the fully control mode, we chose iPad Pro (3rd
	generation), a tablet in iOS 14.3 with a USB Type-C interface, as the target
device in this experiment.  Besides disguising as normal HID devices like a
conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
stream from the target device to the attacker via WiFi.  After the connection
establishment, the attacker performed a series of actions to test the capability of
\tool. In the beginning, the attacker accessed the album application on the iPad and
obtained all the photos inside. After that, the attacker sent messages via victim's
account. At last, the attacker performed a transaction using the
financial application. All of these tests resulted in success.

Through this experiment, we have found that with video transmission and mouse
emulation, \tool extensively expanded the attack capability of BadUSB,
especially in mobile devices. In short, we have archived the complete hijack of the victim's
device in this experiment.
